\documentclass[11pt,letterpaper]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\setlength{\topmargin}{-0.25in}%length of margin at the top of the page (1 inch added by default)
\setlength{\oddsidemargin}{0.0in} %length of margin on sides for odd pages
\setlength{\evensidemargin}{0.0in} %length of margin on sides for even pages
\setlength{\textwidth}{6.5in} %How wide you want your text to be
\setlength{\marginparwidth}{0.5in}
\setlength{\headheight}{0pt} %1in margins at top and bottom (1 inch is added to this value by default)
\setlength{\headsep}{0pt} %Increase to increase white space in between headers and the top of the page
\setlength{\textheight}{9.0in} %How tall the text body is allowed to be on each page
\setlength{\parindent}{0in}
% no page numbers 
\usepackage{nopageno}
\usepackage[none]{hyphenat}
\usepackage[pdfborder={0 0 0},colorlinks=false]{hyperref} 
\usepackage{fancyhdr}
\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{- References Available upon Request -}
\begin{document} 
    \centerline{\LARGE \bf W. Cannon Matthews III} 
    \centerline{ \href{mailto:cannonmatthews@uchicago.edu}{cannonmatthews@uchicago.edu} $\bullet$ 337.962.0644 } 
    \centerline{1005 E. 60th St. \#645 $\bullet$ Chicago, IL 60637 }
    \line(1,0){470} 
%
    \section*{Work Experience} 
        \textbf{UChicago Computer Science Instructional Labratories} \hfill \textit{February 2013 - present }
            \begin{itemize}
            \item Administrer and maintain a lab of 52 OSX and 40 Linux workstations plus supporting servers
            \item Overhauled migration from OSX based servers to virtualized Linux servers, including redevelopemnt and addition of services provided.
            \item In charge of system monitoring and statistical collection, using tools including Nagios, Cacti and custom built solutions. 
            \item Provide helpdesk and tutoring support for students and other users of the lab. 
            \item Diagnosing and Troubleshooting of various issues and problems during lab operation
            \end{itemize}
        \textbf{Louisiana Immersive Technologies Enterprise, Lafayette, LA} \hfill \textit{June 2009 - September 2012} 

       % \vspace{0.1in}
            \begin{footnotesize}
                (\textit{LITE is a 3-D visualization resource center focused on economic development in Louisiana: }\url{http://lite3d.com})
            \end{footnotesize}
            \begin{itemize} 
            \item  Designed, implemented and maintained a database-backed web application to track 
                   employee hours that was used in a production environment. Attained an extensive knowledge of Ruby and the 
                   Ruby on Rails framework, and gained experience with relational databases, particularly MySQL.
            \item  Provided Basic Linux Systems Administration and Help Desk Support as well as installation, configuration and 
                   management of in-house and third-party software and hardware, including virtualized infrastructure, using mainly Gentoo, Fedora and CentOS Linux.
            \item  Worked individually and as part of a team in software development and content creation workflows.
                   Experience using SCRUM/Agile Development practices in a project release cycle. Developed and 
                   released software in a production environment, including bug/issue tracking and unit testing workflows, 
                   and writing API and end user documentation. 
            \end{itemize} 
    \section*{Relevant Skills} 
        \begin{itemize}
        \item Extensive experience with Linux usage and administration in both production and non-production environments,  across several distrobutions (CentOS/RHEL, Fedora, Debian, Gentoo, et al)  
        \item Entry level knowledge and basic experiece with puppet 
        \item Basic experience with and understanding of Virtual Machines and hypervisors, particularly with  VMWare and Xen. 
        \item Extensive experience with various programming and scripting languages including C/C++, Ruby, Python. Bash, and more
        \item Several years experience using command line interfaces and shell scripting. 
        \item Experience with markup languages including HTML/CSS and \LaTeX
        \end{itemize}          
    \section*{Education}
        \textbf{University of Chicago, Chicago, IL } \hfill \textit{ September 2012 - present } 
        \begin{itemize} 
            \item S.B. in Computer Science and S.B. in Math, expected June 2016 
            \item Coursework Includes Major introductory Sequences: CMSC 16100,16200,15400: 
                Honors Intro To Computer Science 1 \& 2, Intro to Systems, and upper level theory and systems classes: 27100,27200,22200
                Discrete Math, Theory of Algorithms and Computer Architecture. 
            \item 3.80 GPA
        \end{itemize}
        \textbf{ Lafayette High School, Lafayette, LA } \hfill \textit{August 2008 - May 2012 }  
        \begin{itemize} 
            \item 4.0\ \  GPA in the  Gifted Program Curriculum
            \end{itemize}
    \vfill
    \centerline{ }
\end{document}
