\documentclass[10pt,letterpaper]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\usepackage[letterpaper,top=0.75in, left=0.75in, right=0.75in, bottom=1in]{geometry}
%\setlength{\topmargin}{-0.25in}%length of margin at the top of the page (1 inch added by default)
%\setlength{\oddsidemargin}{0.0in} %length of margin on sides for odd pages
%\setlength{\evensidemargin}{0.0in} %length of margin on sides for even pages
%\setlength{\textwidth}{7.5in} %How wide you want your text to be
\setlength{\marginparwidth}{0.5in}
%\setlength{\headheight}{0pt} %1in margins at top and bottom (1 inch is added to this value by default)
\setlength{\headsep}{0in} %Increase to increase white space in between headers and the top of the page
%\setlength{\textheight}{9.25in} %How tall the text body is allowed to be on each page
\setlength{\parindent}{0in}
% no page numbers 
\usepackage{nopageno}
\usepackage[none]{hyphenat}
\usepackage[pdfborder={0 0 0},colorlinks=false]{hyperref} 
\usepackage{fancyhdr}
\usepackage[super]{nth} 
\pagestyle{fancyplain}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{
\href{http://cannonmatthews.com}{www.CannonMatthews.com} $\bullet$ \href{https://www.linkedin.com/in/cannonmatthews}{LinkedIn.com/in/cannonmatthews} \\
\href{http://github.com/loosecannon93}{GitHub.com/loosecannon93} $\bullet$ \href{http://stackoverflow.com/users/427447/loosecannon }{StackOverflow.com/users/427447/loosecannon} \\
\vspace{1em}
-- References Available Upon Request --
}
\begin{document} 
    \centerline{\LARGE \bf W. Cannon Matthews III} 
    \centerline{ \href{mailto:cannon@cannonmatthews.com}{cannon@cannonmatthews.com} $\bullet$ \href{tel:13379620644}{337.962.0644 }}
    \centerline{5305 S. Ellis Ave. Unit 3N $\bullet$ Chicago, IL 60615 }
    \hrulefill
%    \line(1,0){470} 
%
    \section*{Education and Honors}
        \textbf{University of Chicago, Chicago, IL} \hfill \textit{ September 2012--Present } 
        \begin{itemize} 
            \item Dual S.B. in Computer Science and Mathematics, expected June 2016. 
            \item Completed coursework in the Computer Science and Mathematics departments including: Discrete Math, Algorithms, Complexity Theory, Computer Architecture, Networks, Operating Systems, Scientific Visualization, Abstract Algebra and Real Analysis.  
            \item 3.808 overall GPA. Dean's List: 2012--13, 2013--14, 2014--15 academic years. 
        \end{itemize}
        \textbf{Illinois Technology Association} -- \href{http://www.chicagotribune.com/bluesky/originals/chi-university-of-chicago-student-wins-tech-challenge-bsi-story.html}{\nth{1} place -- 2014 Tech Challenge Finals} \hfill \textit{November 7, 2014} 
        \vspace{0.5em}\\
        \textbf{Lafayette High School, Lafayette, LA} -- 4.0 GPA Gifted Curriculum \hfill \textit{Graduated May 2012 } 
%    \vfill
    \section*{Relevant Professional Experience} 
        \textbf{Google, Inc. --- Software Engineering Intern} \hfill \textit{June 2015--September 2015} 
            \begin{itemize} 
            \item Improved system for ranking POIs on maps using machine trained models based on location categories. Contributed to a production release of the ranker.
            \end{itemize} 
            \vspace{1em}
        \textbf{University of Chicago Computer Science Instructional Laboratories} (CSIL) \hfill \textit{February 2013--Present }
            \begin{footnotesize}
                (\url{http://csil.cs.uhicago.edu})
            \end{footnotesize}
            \begin{itemize}
            \item Oversee a lab of 52 OSX and 40 Linux workstations and additional servers on an ongoing basis.
            \item Led the overhaul of CSIL's server platform in a migration from Apple OSX systems to virtualized Linux servers, including structural redevelopment to facilitate the addition of services provided to lab users \textit{(Summer 2013)}. 
            \item Currently in charge of system monitoring and collection of usage statistics on the CSIL machines, using custom-built solutions as well as off-the-shelf tools including Nagios, Cacti, Rsyslog and others. 
            \end{itemize}
            \vspace{1em}

        \textbf{Louisiana Immersive Technologies Enterprise, Lafayette, LA} (LITE) \hfill \textit{June 2009--September 2012} 

            \begin{footnotesize}
                (\textit{LITE is a 3-D visualization resource center focused on economic development in Louisiana: }\url{http://lite3d.com})
            \end{footnotesize}
            \begin{itemize} 
            \item  Designed, implemented and maintained a database-backed web application that was used in a production environment to track 
                   employee hours. Developed an extensive knowledge of Ruby and the 
                   Ruby on Rails framework, as well as relational databases, particularly MySQL.
            \item  Provided basic Linux Systems Administration and Helpdesk Support as well as installation, configuration and 
                   management of in-house and third-party software and hardware, including virtualized infrastructure.
            \end{itemize} 
    \section*{Technical Skills} 
        \begin{itemize}
        \item Skilled in a variety of areas covering both software development and systems administration. 
        \item Proficient with multiple programming and scripting languages including C, C++, Python, Bash, Ruby \& SQL in addition to markup languages such as HTML and \LaTeX.
        \item Extensive experience with Linux administration in both production and non-production environments, across several distributions, 
        including a working knowledge of the Ansible configuration management system.
        \item Thorough knowledge and experience with virtual machines and hypervisors, using VMware, KVM, and Xen. 
        \end{itemize}          
\end{document}

